Characterisation of MSC in clinical trial reports: analysis of published descriptors

### 2020-09-04 paper2_figures.Rmd
fig updates
fig formatting for SCTM

---
title: 'Characterisation of MSC in clinical trial reports: analysis of published descriptors'
author: "Emma Rand"
date: "16/01/2020"
output:
  html_document: default
  wmf_document: default
---

@@

Fit on single 8.5" × 11" or A4 paper
Preferably at:
1 column - 3.5 inches
1.5 columns - 5.0 inches
2 columns = 7.3 inches

@@

```{r pkg}
library(tidyverse)
# library(readxl)
# library(kableExtra)
library(grid)
library(patchwork)
library(janitor)

@@

# palette
pal <- viridisLite::viridis(6)

# figure saving settings
units = "in"
fig_w <- 3.5 # one col
fig_w_1.5 <- 5 # 1.5 col
fig_w_2 <- 7.3 # 2 col
fig_h <- fig_w

@@

### each panel of fig 1
```{r fig1}
# figure 1 a
article_funnel <- to_poly_orig %>%
  ggplot() +
  geom_polygon(aes(x,
                   y,
                   group = group,
                   fill = step_names),
               size = 0) +
  geom_label(aes(x = 0,
                y = y,
                label = n),
            data = labels, 
            size = 3,
            label.size = 0,
            label.padding = unit(0.1, "lines"),
            label.r = unit(0.1, "lines")) +
  scale_y_continuous(breaks = labels$y,
                     labels = labels$step_names2) +
  theme_minimal() +
  theme(legend.position = "none",
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y  = element_text(size = 7, colour = "black", hjust = 0, face = "plain"),
        panel.spacing = unit(0, "lines"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank()) +
    scale_fill_manual(values = rev(pal))

@@

data_collection <- fig1b %>% 
  ggplot() +
  geom_text(aes(x = x, y = y, label = item),
            size = 2.5,nudge_y = 0.1,
            hjust = "left") +
  facet_grid(. ~ data_element) +
  scale_x_continuous(limits = c(0, 7)) +
  theme_minimal() +
  theme(legend.position = "none",
        strip.text = element_text(hjust = 0, size = 5.5, colour = "white", face = "bold"),
        strip.background = element_rect(fill = pal[1], colour = pal[1], size = 0.05),
        panel.border = element_rect(colour = "black", fill = NA),
        panel.spacing = unit(0, "lines"),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

@@

fig1 <- article_funnel + data_collection + 
  plot_layout(design = layout) +
  plot_annotation(tag_levels = "A") &
    theme(plot.tag = element_text(size = 9, hjust = 1, face = "bold"))

ggsave("figs/fig_1.wmf", 
       plot = fig1, 
       device = "wmf",
       width = fig_w, 
       height = fig_h*1.6,
       units = units)

@@

### each panel figure 2
```{r fig2}
#by country
country_bar <- summary_country %>% 
  ggplot(aes(x = reorder(country, n), y = n)) +
  geom_bar(stat = "identity", 
           # fill = pal[4],
           fill = "black",
           size = 0, width = 0.8) +
  xlab("") +
  scale_y_continuous(name = NULL, 
                     breaks = seq(0, 15, 5),
                     minor_breaks = seq(0, 15, 1),
                     limits = c(0, 16),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

# by phase
phase_bar <- summary_phase %>% 
  ggplot(aes(x = reorder(phase,n), y = n)) +
  geom_bar(stat = "identity", 
           # fill = pal[4],
           fill = "black",
           size = 0, 
           width = 0.8) +
  xlab("") +
 # geom_text(aes(y = n + 4, label = pc) ) +
  scale_y_continuous(name = NULL, 
                     breaks = seq(0, 20, 10),
                     minor_breaks = seq(0, 20, 1),
                     limits = c(0, 25),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

# by indication
indication_bar <- summary_indication %>% 
  ggplot(aes(x = reorder(indication, n), y = n)) +
  geom_bar(stat = "identity", 
           # fill = pal[4], 
           fill = "black", 
           size = 0, 
           width = 0.8) +
  xlab("") +
  scale_y_continuous(name = NULL, 
                     breaks = seq(0, 12, 2),
                     minor_breaks = seq(0, 12, 2),
                     limits = c(0, 13),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

# by route
route_bar <- summary_route %>% 
  ggplot(aes(x = reorder(route, n), y = n)) +
  geom_bar(stat = "identity", 
           # fill = pal[4],
            fill = "black",
           size = 0, 
           width = 0.8) +
  xlab("") +
#  geom_text(aes(y = n + 3, label = pc) ) +
  scale_y_continuous(name = NULL, 
                     breaks = seq(0, 25, 5),
                     minor_breaks = seq(0, 25, 1),
                     limits = c(0, 25),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

@@

fig2 <- country_bar + phase_bar + route_bar + indication_bar +
  plot_layout(design = layout) +
  plot_annotation(caption = "Number of Articles",
                  tag_levels = "A")&
    theme(plot.tag = element_text(size = 9, hjust = 0, face = "bold"),
          plot.caption = element_text(size = 9, hjust = 0.5, face = "plain"))

ggsave("figs/fig_2_black.wmf", 
       plot = fig2, 
       device = "wmf",
       width = fig_w_2, 
       height = fig_h*2,
       units = units)

@@

```{r fig_3}
# source
source_bar <- summary_source %>% 
  ggplot(aes(x = source, y = n)) +
  geom_bar(stat = "identity",
           # fill = pal[4],
           fill = "black",
           size = 0, 
           width = 0.8) +
  scale_y_continuous(name = "Number of Articles",
                    breaks = seq(0, 50, 10),
                    minor_breaks = seq(0, 50, 10),
                    limits = c(0, 60),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = NULL) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black",
                                  angle = 285, vjust = 0.5, hjust = 0),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank())

@@

fig3 <- source_bar  + allo_auto_bar + stem_stromal_bar +
  plot_layout(design = layout) +
  plot_annotation(caption = "Source",
                  tag_levels = "A") &
    theme(plot.tag = element_text(size = 9, hjust = 0, face = "bold"),
          plot.caption = element_text(size = 9, hjust = 0.5, vjust = 1, face = "plain"))

ggsave("figs/fig_3_black.wmf", 
       plot = fig3, 
       device = "wmf",
       width = fig_w_1.5, 
       height = fig_h,
       units = units)
```

@@

```{r fig_4}
# test stringency overall
test_bar <- summary_test %>% 
  ggplot(aes(x = test_results, y = n, fill = test_results)) +
  geom_bar(stat = "identity", size = 0) +
  xlab("") +
  geom_text(aes(y = n + 6, label = pc), size = 3 ) +
  scale_fill_manual(values = rev(pal[1:5]),
                    name = "Test results") +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 50, 5),
                     minor_breaks = seq(0, 50, 1),
                     limits = c(0, 53),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), ) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        plot.margin = margin(t = 0, r = 30),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.position = "none") +
  coord_flip()

# tests stringency by phase
phase_test <- summary_phase_test %>% 
  ggplot(aes(x = phase_condensed, y = n, fill = test_results)) +
  geom_bar(stat = "identity", size = 0, width = 0.8) +
  scale_fill_manual(values = pal,
                    name = NULL) +
  scale_y_continuous(name = "Number of Articles",
                     breaks = seq(0, 55, 10),
                     minor_breaks = seq(0, 55, 5),
                     limits = c(0, 55),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Phase") +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        plot.margin = margin(t = 0, r = 0, l = 0),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.position = "none")

# 
markerp_bar <- summary_marker_p_count %>% 
  ggplot(aes(x = marker_p_count, y = n)) +
  geom_bar(stat = "identity", fill = "black", size = 0, width = 0.8) +
  scale_y_continuous(name = NULL, 
                     breaks = seq(0, 12, 2),
                     minor_breaks = seq(0, 12, 2),
                     limits = c(0, 12),
                     expand = c(0, 0)) +
  scale_x_continuous(name = "Number of markers",
                     breaks = seq(0, 11, 1),
                    minor_breaks = seq(0, 12, 2),
                    limits = c(0.5, 12),
                     expand = c(0, 0)) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.margin = margin(t = 0, r = 0, l = 0))

@@

layout <- "
aaaaaabbbcccc
"

fig4 <- test_bar + phase_test + markerp_bar +
  plot_layout(design = layout) +
  plot_annotation(tag_levels = "A") &
    theme(plot.tag = element_text(size = 9, hjust = 0, face = "bold"))

ggsave("figs/fig_4.wmf", 
       plot = fig4, 
       device = "wmf",
       width = fig_w_2, 
       height = 2.2,
       units = units)
```

@@

fig5b <- test_by_attribute_summary %>% 
  ggplot() +
  geom_bar(aes(x = n, y = marker2, fill = test_status),
           stat = "identity", width = 0.8, size = 0) +
  scale_fill_manual(values =  c("#BABABA", pal[c(3, 5)])) +
  scale_x_continuous(name = "Number of Articles",
                     breaks = seq(0, 90, 10),
                     minor_breaks = seq(0, 90, 10),
                     limits = c(0, 85),
                     expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0.5), name = NULL, labels = codes$ISCT) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 10, colour = "black",
                                    face = "bold", vjust = 0.3),
        axis.ticks.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        legend.position = "none")

@@

fig5 <- fig5a + fig5b &
  plot_layout(design = layout) &
  plot_annotation(tag_levels = "A") &
  geom_hline(yintercept = 1.5) &
   geom_hline(yintercept = 11.5) &
    theme(plot.tag = element_text(size = 9, hjust = 0, face = "bold"),
          plot.margin = margin(0,0,0,0))

ggsave("figs/fig_5.wmf", 
       plot = fig5, 
       device = "wmf",
       width = fig_w_2, 
       height = fig_h * 1.2,
       units = units)
```

@@

```{r}
# panel a
fig6a <- functionality %>% 
  ggplot() +
  geom_bar(aes(x = type, y = n, fill = status, label = pc),
           stat = "identity", size = 0) +
  scale_fill_manual(values =  c("#BABABA", pal[c(3, 5)]),
                    name = " Functionality",
                    guide = guide_legend(nrow = 4,
                                         title.position = "top",
                                         title.hjust = 0 )) +
  scale_y_continuous(name = "Number of Articles",
                     breaks = seq(0, 80, 10),
                     minor_breaks = seq(0, 80, 10),
                     limits = c(0, 85),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0.5), name = NULL) +
  geom_text(data = filter(functionality, 
                          status == "Not mentioned"),
            aes(x = type, 50, label = pc) ) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        plot.margin = margin(t = 0, r = 30),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.position = "top",
        legend.text = element_text(size = 8, colour = "black"),
        legend.key.size = unit(0.1, "in")) +
  coord_flip()

# panel b
fig6b <- moa_isct_summary %>% 
  ggplot(aes(x = MOA, y = n, fill = stem_stromal)) +
  geom_bar(stat = "identity", size = 0) +
  scale_fill_manual(values = pal, 
                    name = "Nomenclature",
                    guide = guide_legend(nrow = 4,
                                         title.position = "top",
                                         title.hjust = 0 )) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 30, 5),
                     minor_breaks = seq(0, 30, 5),
                     limits = c(0, 35),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "MOA") +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        plot.margin = margin(t = 0, r = 0, l = 0),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.position = "top",
        legend.text = element_text(size = 8, colour = "black"),
        legend.key.size = unit(0.1, "in")) +
  coord_flip()

>>>>

---
title: 'Characterisation of MSC in clinical trial reports: analysis of published descriptors'
author: "Emma Rand"
date: "16/01/2020"
output:
  html_document: default
  tiff_document: default
---

@@

fig size for SCTM
height no more than 9.6 inches
Preferably at:
1 column - 3.2 inches
1.5 columns - 4.5 inches
2 columns = 5.8 inches

@@

```{r pkg}
library(tidyverse)
# library(readxl)
# library(kableExtra)
library(grid)
library(patchwork)
library(janitor)
library(showtext)

@@

```{r}
#showtext_auto()
conv <- 0.352778
# palette
pal <- viridisLite::viridis(6)

# figure saving settings
units = "in"
fig_w <- 3.2 # one col
fig_w_1.5 <- 4.5 # 1.5 col
fig_w_2 <- 5.8 # 2 col
fig_h <- fig_w

@@

### each panel of fig 1
```{r fig1}
# figure 1 a
article_funnel <- to_poly_orig %>%
  ggplot() +
  geom_polygon(aes(x,
                   y,
                   group = group,
                   fill = step_names),
               size = 0) +
  geom_label(aes(x = 0,
                y = y,
                label = n),
            data = labels, 
            size = 3,
            label.size = 0,
            label.padding = unit(0.1, "lines"),
            label.r = unit(0.1, "lines")) +
  scale_y_continuous(breaks = labels$y,
                     labels = labels$step_names2) +
  theme_minimal() +
  theme(text = element_text(family = "Calibri", size = 8),
        legend.position = "none",
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y  = element_text(colour = "black", hjust = 0, face = "plain"),
        panel.spacing = unit(0, "lines"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank()) +
    scale_fill_manual(values = rev(pal))

@@

data_collection <- fig1b %>% 
  ggplot() +
  geom_text(aes(x = x, y = y, label = item),
            size = 2.5,nudge_y = 0.1,
            hjust = "left") +
  facet_grid(. ~ data_element) +
  scale_x_continuous(limits = c(0, 7)) +
  theme_minimal() +
  theme(text = element_text(family = "Calibri", size = 10),
        legend.position = "none",
        strip.text = element_text(size = 8, hjust = 0, colour = "white", face = "bold"),
        strip.background = element_rect(fill = pal[1], colour = pal[1], size = 0.05),
        panel.border = element_rect(colour = "black", fill = NA),
        panel.spacing = unit(0, "lines"),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

@@

fig1 <- article_funnel + data_collection + 
  plot_layout(design = layout) +
  plot_annotation(tag_levels = "A",
                  title = "Wilson, Alison, Figure 1. TOP") &
    theme(plot.tag = element_text(size = 12,
                                  hjust = 1,
                                  face = "bold",
                                  family = "Calibri"),
        plot.title = element_text(size = 6))

ggsave("figs/fig_1.tiff", 
       plot = fig1, 
       device = "tiff",
       width = fig_w_1.5, 
       height = fig_h*1.8,
       units = units)

@@

### each panel figure 2
```{r fig2}
#by country
country_bar <- summary_country %>% 
  ggplot(aes(x = reorder(country, n), y = n)) +
  geom_bar(stat = "identity", 
           # fill = pal[4],
           fill = "black",
           size = 0, width = 0.8) +
  xlab("") +
  scale_y_continuous(name = NULL, 
                     breaks = seq(0, 15, 5),
                     minor_breaks = seq(0, 15, 1),
                     limits = c(0, 16),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  theme_classic() +
  theme(text = element_text(family = "Calibri"),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

# by phase
phase_bar <- summary_phase %>% 
  ggplot(aes(x = reorder(phase,n), y = n)) +
  geom_bar(stat = "identity", 
           # fill = pal[4],
           fill = "black",
           size = 0, 
           width = 0.8) +
  xlab("") +
 # geom_text(aes(y = n + 4, label = pc) ) +
  scale_y_continuous(name = NULL, 
                     breaks = seq(0, 20, 10),
                     minor_breaks = seq(0, 20, 1),
                     limits = c(0, 25),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  theme_classic() +
  theme(text = element_text(family = "Calibri"),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

# by indication
indication_bar <- summary_indication %>% 
  ggplot(aes(x = reorder(indication, n), y = n)) +
  geom_bar(stat = "identity", 
           # fill = pal[4], 
           fill = "black", 
           size = 0, 
           width = 0.8) +
  xlab("") +
  scale_y_continuous(name = NULL, 
                     breaks = seq(0, 12, 2),
                     minor_breaks = seq(0, 12, 2),
                     limits = c(0, 13),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  theme_classic() +
  theme(text = element_text(family = "Calibri"),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

# by route
route_bar <- summary_route %>% 
  ggplot(aes(x = reorder(route, n), y = n)) +
  geom_bar(stat = "identity", 
           # fill = pal[4],
            fill = "black",
           size = 0, 
           width = 0.8) +
  xlab("") +
#  geom_text(aes(y = n + 3, label = pc) ) +
  scale_y_continuous(name = NULL, 
                     breaks = seq(0, 25, 5),
                     minor_breaks = seq(0, 25, 1),
                     limits = c(0, 25),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  theme_classic() +
  theme(text = element_text(family = "Calibri"),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

@@

fig2 <- country_bar + phase_bar + route_bar + indication_bar +
  plot_layout(design = layout) +
  plot_annotation(caption = "Number of Articles",
                  tag_levels = "A",
                  title = "Wilson, Alison, Figure 2. TOP") &
    theme(plot.tag = element_text(size = 12,
                                  hjust = 1,
                                  face = "bold",
                                  family = "Calibri"),
         plot.title = element_text(size = 6),
         plot.caption.position = "plot",
         plot.caption = element_text(hjust = 0.5, size = 12))

ggsave("figs/fig_2_black.tiff", 
       plot = fig2, 
       device = "tiff",
       width = fig_w_2, 
       height = fig_h*2.2,
       units = units)

@@

```{r fig_3}
# source
source_bar <- summary_source %>% 
  ggplot(aes(x = source, y = n)) +
  geom_bar(stat = "identity",
           # fill = pal[4],
           fill = "black",
           size = 0, 
           width = 0.8) +
  scale_y_continuous(name = "No. Articles",
                    breaks = seq(0, 50, 10),
                    minor_breaks = seq(0, 50, 10),
                    limits = c(0, 60),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = NULL) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black",
                                  angle = 285, vjust = 0.5, hjust = 0),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank())

@@

fig3 <- source_bar  + allo_auto_bar + stem_stromal_bar +
  plot_layout(design = layout) +
  plot_annotation(caption = "Source",
                  tag_levels = "A",
                  title = "Wilson, Alison, Figure 3. TOP") &
    theme(plot.tag = element_text(size = 12, 
                                  hjust = 0, 
                                  face = "bold",
                                  family = "Calibri"),
          plot.title = element_text(size = 6),
          plot.caption = element_text(size = 12, 
                                      hjust = 0.5, 
                                      vjust = 1, 
                                      family = "Calibri"))

ggsave("figs/fig_3_black.tiff", 
       plot = fig3, 
       device = "tiff",
       width = fig_w_1.5, 
       height = fig_h,
       units = units)
```

@@

```{r fig_4}
# test stringency overall
test_bar <- summary_test %>% 
  ggplot(aes(x = test_results, y = n, fill = test_results)) +
  geom_bar(stat = "identity", size = 0) +
  xlab("") +
  geom_text(aes(y = n + 7, label = pc), size = 2.5 ) +
  scale_fill_manual(values = rev(pal[1:5]),
                    name = "Test results") +
  scale_y_continuous(name = "No. Articles", 
                     breaks = seq(0, 50, 10),
                     minor_breaks = seq(0, 50, 1),
                     limits = c(0, 55),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), ) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        plot.margin = margin(t = 0, r = 20, l = 0),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.position = "none") +
  coord_flip()

# tests stringency by phase
phase_test <- summary_phase_test %>% 
  ggplot(aes(x = phase_condensed, y = n, fill = test_results)) +
  geom_bar(stat = "identity", size = 0, width = 0.8) +
  scale_fill_manual(values = pal,
                    name = NULL) +
  scale_y_continuous(name = "No. Articles",
                     breaks = seq(0, 55, 10),
                     minor_breaks = seq(0, 55, 5),
                     limits = c(0, 55),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Phase") +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        plot.margin = margin(t = 0, r = 0, l = 0),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.position = "none")

# 
markerp_bar <- summary_marker_p_count %>% 
  ggplot(aes(x = marker_p_count, y = n)) +
  geom_bar(stat = "identity", fill = "black", size = 0, width = 0.8) +
  scale_y_continuous(name = NULL, 
                     breaks = seq(0, 12, 2),
                     minor_breaks = seq(0, 12, 2),
                     limits = c(0, 12),
                     expand = c(0, 0)) +
  scale_x_continuous(name = "No. markers",
                     breaks = seq(0, 11, 1),
                    minor_breaks = seq(0, 12, 2),
                    limits = c(0.5, 12),
                     expand = c(0, 0)) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 6, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.margin = margin(t = 0, r = 1, l = 0))

@@

layout <- "
aaaaaabbbccccc
"

fig4 <- test_bar + phase_test + markerp_bar +
  plot_layout(design = layout) +
  plot_annotation(tag_levels = "A",
                  title = "Wilson, Alison, Figure 4. TOP") &
    theme(plot.tag = element_text(size = 12,
                                  hjust = 1,
                                  face = "bold",
                                  family = "Calibri"),
         plot.title = element_text(size = 6))

ggsave("figs/fig_4.tiff", 
       plot = fig4, 
       device = "tiff",
       width = fig_w_2, 
       height = 2.2,
       units = units)
```

@@

fig5b <- test_by_attribute_summary %>% 
  ggplot() +
  geom_bar(aes(x = n, y = marker2, fill = test_status),
           stat = "identity", width = 0.8, size = 0) +
  scale_fill_manual(values =  c("#BABABA", pal[c(3, 5)])) +
  scale_x_continuous(name = "No. Articles",
                     breaks = seq(0, 90, 10),
                     minor_breaks = seq(0, 90, 10),
                     limits = c(0, 85),
                     expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0.5), name = NULL, labels = codes$ISCT) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 10, colour = "black",
                                    face = "bold", vjust = 0.3),
        axis.ticks.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        legend.position = "none")

@@

fig5 <- fig5a + fig5b &
  plot_layout(design = layout) &
  plot_annotation(tag_levels = "A",
                  title = "Wilson, Alison, Figure 5. TOP") &
  geom_hline(yintercept = 1.5) &
   geom_hline(yintercept = 11.5) &
    theme(plot.tag = element_text(size = 12, 
                                  hjust = 0,
                                  face = "bold",
                                  family = "Calibri"),
          plot.title = element_text(size = 6),
          plot.margin = margin(0,0,0,0))

ggsave("figs/fig_5.tiff", 
       plot = fig5, 
       device = "tiff",
       width = fig_w_2, 
       height = fig_h * 1.2,
       units = units)
```

@@

```{r}
# panel a
fig6a <- functionality %>% 
  ggplot() +
  geom_bar(aes(x = type, y = n, fill = status, label = pc),
           stat = "identity", size = 0) +
  scale_fill_manual(values =  c("#BABABA", pal[c(3, 5)]),
                    name = " Functionality",
                    guide = guide_legend(nrow = 4,
                                         title.position = "top",
                                         title.hjust = 0 )) +
  scale_y_continuous(name = "No. Articles",
                     breaks = seq(0, 80, 20),
                     minor_breaks = seq(0, 80, 10),
                     limits = c(0, 85),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0.5), name = NULL) +
  geom_text(data = filter(functionality, 
                          status == "Not mentioned"),
            aes(x = type, 50, label = pc) ) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        axis.title = element_text(size = 8, colour = "black"),
        plot.margin = margin(t = 0, r = 30),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.position = "top",
        legend.text = element_text(size = 8, colour = "black"),
        legend.title = element_text(size = 8, colour = "black"),
        legend.key.size = unit(0.1, "in")) +
  coord_flip()

# panel b
fig6b <- moa_isct_summary %>% 
  ggplot(aes(x = MOA, y = n, fill = stem_stromal)) +
  geom_bar(stat = "identity", size = 0) +
  scale_fill_manual(values = pal, 
                    name = "Nomenclature",
                    guide = guide_legend(nrow = 4,
                                         title.position = "top",
                                         title.hjust = 0 )) +
  scale_y_continuous(name = "No. Articles", 
                     breaks = seq(0, 30, 5),
                     minor_breaks = seq(0, 30, 5),
                     limits = c(0, 35),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "MOA") +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        axis.title = element_text(size = 8, colour = "black"),
        plot.margin = margin(t = 0, r = 0, l = 0),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.position = "top",
        legend.text = element_text(size = 8, colour = "black"),
        legend.title = element_text(size = 8, colour = "black"),
        legend.key.size = unit(0.1, "in")) +
  coord_flip()

# panel c
fig6c <- diffmoasum %>%
  ggplot(aes(x = MOA, y = n, fill = differentiation)) +
  geom_bar(stat = "identity", size = 0) +
   scale_fill_manual(values = c("#BABABA", pal[5]), 
                    name = "Differentiation capacity",
                    labels = c("Not demonstrated", "Demonstrated"),
                    guide = guide_legend(nrow = 4, 
                                         title.position = "top",
                                         title.hjust = 0)) +
  scale_y_continuous(name = "No. Articles", 
                     breaks = seq(0, 30, 5),
                     minor_breaks = seq(0, 30, 5),
                     limits = c(0, 35),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = NULL, labels = NULL) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        axis.title = element_text(size = 8, colour = "black"),
        plot.margin = margin(t = 0, r = 0, l = 0),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.position = "top",
        legend.text = element_text(size = 8, colour = "black"),
        legend.title = element_text(size = 8, colour = "black"),
        legend.key.size = unit(0.1, "in")) +
  coord_flip()
